Tracing Hidden Struggles of Rural Indian Women during Pandemic

### 2024-04-16 outputs/paper.qmd
ONLY PAPER

# Prepare data
data$geo_state <- as.factor(data$geo_state)
data$geo_district <- as.factor(data$geo_district)
data$final_status <- as_factor(data$final_status)
# Figure 1a: Histogram of Income
p1a <- ggplot(data, aes(x = tran_inc_normal)) +
  geom_histogram(aes(y = ..density..), color = "gray", fill = "gray", bins = 30) +
  geom_histogram(data = data, aes(x = tran_inc_current, y = ..density..), 
                 color = "black", fill = NA, bins = 30) +
  labs(title = "Distributions of Transformed Income",
       x = "Inverse Hyperbolic Sin of Income (in Rs.)",
       y = "Density") +
  scale_fill_manual(values = c("gray", "black"),
                    labels = c("Normal Month", "Current Month")) +
  scale_color_manual(values = c("gray", "black"),
                     labels = c("Normal Month", "Current Month")) +
  theme(legend.title = element_blank(), legend.position = "bottom")

ggsave("/cloud/project/outputs/figures/fig1a.png", plot = p1a, width = 10, height = 8, dpi = 300)

@@

ggsave(paste0(output_path, "/figures/fig1b.png"), plot = coef_plot, width = 10, height = 5, dpi = 300)

>>>>

# Prepare data
data$geo_state <- as.factor(data$geo_state)
data$geo_district <- as.factor(data$geo_district)
data$final_status <- as_factor(data$final_status)
# Figure 1a: Histogram of Income
p1a <- ggplot(data, aes(x = tran_inc_normal)) +
  geom_histogram(aes(y = after_stat(density)), color = "gray", fill = "gray", bins = 30) +
  geom_histogram(data = data, aes(x = tran_inc_current, y = after_stat(density)), 
                 color = "black", fill = NA, bins = 30) +
  labs(title = "Distributions of Transformed Income",
       x = "Inverse Hyperbolic Sin of Income (in Rs.)",
       y = "Density") +
  scale_fill_manual(values = c("gray", "black"),
                    labels = c("Normal Month", "Current Month")) +
  scale_color_manual(values = c("gray", "black"),
                     labels = c("Normal Month", "Current Month")) +
  theme(legend.title = element_blank(), legend.position = "bottom")

@@
